Trait pleiotropy of regulatory variants increases with the variety of bound transcription factors, regulated genes and active tissues

### 2022-09-13 ms/ms05_floats.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 2: Fisher stat of tissues in variants as a function of gwas category count
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.66\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_tissue_enrich_in_pleio.py/plt.png}
\end{subfigure}
%
\caption{Tissue category odds ratio in pleitropic variants compared with variant with GWAS category count 1.} \label{fig:tissues}
\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Tab 2: Winner regions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{subfigure}[]{.32\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories9.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr17_start39548459_end40421164_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr17_start48116861_end49436349_categories8.png}
\end{subfigure}

\begin{subfigure}[]{.32\textwidth}
\textbf{g}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories9.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr17_start39548459_end40421164_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr17_start48116861_end49436349_categories8.png}
\end{subfigure}

\caption{Count of GWAS categories (\textbf{a-c}), eGenes (\textbf{d-f}) and eTissues (\textbf{g-i}) in three pleiotropic genomic regions: \textbf{a,d,g}: 5:132,239,645-132,497,907 (5q31.1), \textbf{b,e,h}: 6:31,034,839-32,478,149 (6p21.33) and \textbf{c,g,i}: 12:111,395,984-111,645,358 (12q24.1). Genomic coordinates are given for the hg38 assembly.} \label{fig:region_gwas_egenes_tissues}
%
\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 3: VEP consequences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{figure*}[!tbp]
%\centering
%%
%\begin{subfigure}[]{.32\textwidth}
%\textbf{a}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/missense_variant.png}
%%
%\end{subfigure}
%%
%\begin{subfigure}[]{.32\textwidth}
%\textbf{b}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/splice_region_variant.png}
%%
%\end{subfigure}
%%
%\begin{subfigure}[]{.32\textwidth}
%\textbf{c}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/3_prime_UTR_variant.png}
%%
%\end{subfigure}
%%
%\caption{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: \textbf{a}, Missense variant, \textbf{b}, splice region variant and \textbf{c}, 3' UTR variant.} \label{fig:vep_consequence}
%%
%\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 4: Violin plots. eGenes, eTissues and gwas per variants
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of eGenes per variant-tissue (\textbf{a}), eTissues per variant-eGene (\textbf{b}) and GWAS categories per variant-eGene-eTissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 6: TF count per GWAS category count
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% Fig 2: Fisher stat of tissues in variants as a function of gwas category count
%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\begin{figure*}[!tbp]
%\centering
%%
%\begin{subfigure}[]{.66\textwidth}
%\textbf{a}
%\\
%\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_tissue_enrich_in_pleio.py/plt.png}
%\end{subfigure}
%%
%\caption{Tissue category odds ratio in pleitropic variants compared with variant with GWAS category count 1.} \label{fig:tissues}
%\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Tab 2: Winner regions
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{subfigure}[]{.32\textwidth}
\textbf{d}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr5_start131912097_end132802472_categories9.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{e}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr17_start39548459_end40421164_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{f}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_egene.py/count_per_rsid_chr17_start48116861_end49436349_categories8.png}
\end{subfigure}

\begin{subfigure}[]{.32\textwidth}
\textbf{g}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr5_start131912097_end132802472_categories9.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{h}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr17_start39548459_end40421164_categories8.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{i}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltsctr_x_per_rsid_y_etissue.py/count_per_rsid_chr17_start48116861_end49436349_categories8.png}
\end{subfigure}

\caption{Count of GWAS categories (\textbf{a-c}), eGenes (\textbf{d-f}) and eTissues (\textbf{g-i}) in three pleiotropic genomic regions: \textbf{a,d,g}: 5:132,239,645-132,497,907 (5q31.1), \textbf{b,e,h}: 6:31,034,839-32,478,149 (6p21.33) and \textbf{c,g,i}: 12:111,395,984-111,645,358 (12q24.1). Genomic coordinates are given for the hg38 assembly.} \label{fig:region_gwas_egenes_tissues}
%
\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 3: VEP consequences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/upstream_gene_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/intron_variant.png}
%
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/3_prime_UTR_variant.png}
%
\end{subfigure}
%
\caption{Variant effect predictor (VEP) analysis as a function of the number of GWAS catategory number for three different consequences: \textbf{a}, Upstream gene variant, \textbf{b}, intron variant and \textbf{c}, 3' UTR variant.} \label{fig:vep_consequence}
%
\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 4: Violin plots. eGenes, eTissues and gwas per variants
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{figure*}[!tbp]
\centering
%
\begin{subfigure}[]{.32\textwidth}
\textbf{a}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_etissue_y_egene.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{b}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_y_etissue.py/plt.png}
\end{subfigure}
%
\begin{subfigure}[]{.32\textwidth}
\textbf{c}
\\
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_x_per_variant_egene_etissue_y_gwas.py/plt.png}
\end{subfigure}
%
\caption{Count of eGenes per variant-tissue (\textbf{a}), eTissues per variant-eGene (\textbf{b}) and GWAS categories per variant-eGene-eTissue (\textbf{c}).} \label{fig:gwas_egene_etisue_per_variant}
%
\end{figure*}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 6: TF count per GWAS category count
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
